---
title: "lasso ridge"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list = ls(all=TRUE))
```

```{r}
setwd("C:/Users/prithvi/Desktop/connect")
connect_data=read.csv("connect-4.csv")
```

```{r}
result=connect_data$win
connect_data1=cbind(connect_data,result)
connect_data1$win=NULL
```

```{r}
library(dummies)
connect_data2=dummy.data.frame(connect_data1[,-43])
str(connect_data2)
```

```{r}
connect_data3=cbind(connect_data2,result)
```

```{r}
library(caret)
set.seed(123)
train_rows <- createDataPartition(connect_data3$result, p = 0.7, list = F)

train_data <- connect_data3[train_rows,]

test_data <-connect_data3[-train_rows,]
str(train_data)
```

```{r}
table(train_data$result)

train1<-train_data[train_data$result=='win'|train_data$result=='draw',]

```

```{r}
table(train1$result)
train1$result<-factor(train1$result)
```

```{r}
library(DMwR)
attach(train1)
smote_data1=SMOTE(result  ~.,train1,perc.over =400 ,k=5,perc.under = 100,learner = NULL)
table(smote_data1$result)
```

```{r}
train2<-train_data[train_data$result=='win'|train_data$result=='loss',]
train2$result<-factor(train2$result)
table(train2$result)
```

```{r}
library(DMwR)
attach(train2)
smote_data2=SMOTE(result ~.,train2,perc.over =150 ,k=5,perc.under = 100,learner = NULL)
table(smote_data2$result)
```

```{r}
smote_data<-rbind(smote_data1,smote_data2[smote_data2$result=='loss',])
write.csv(smote_data,file = "file:///C:/Users/prithvi/Desktop/connect/smote_data1.csv")
wite.csv(test_data,file="file:///C:/Users/prithvi/Desktop/connect/test_data.csv")

smote_data=read.csv("file:///C:/Users/prithvi/Desktop/connect/smote_data1.csv")
test_data=read.csv("file:///C:/Users/prithvi/Desktop/connect/test_data.csv")
```


```{r}
summary(smote_data)
```
#Lasso Model
```{r}

library(glmnet)
x=model.matrix(smote_data$result~.,smote_data)
head(x)
fit.lasso <- glmnet(x, smote_data$result, family="multinomial", alpha=1)
```
## Plots for Different Lambda
```{r}
plot(fit.lasso,xvar="lambda",main="LASSO")
```
##Cross Validation for Lasso 
```{r}
fit.lasso.cv <- cv.glmnet(x,smote_data$result, type.measure="class", alpha=1, 
                          family="multinomial",nfolds=10,parallel=TRUE)

```
## Predicting the Min Lambda
```{r}
x.train = model.matrix(smote_data$result~.,smote_data)
pred.lasso.csv <- predict(fit.lasso.cv,x.train,s = fit.lasso.cv$lambda.min)

plot(fit.lasso, xvar="lambda")
```
Perform the model with the lambda min choosen 
```{r}
fit.lasso.cv$lambda.min
fit.lasso1 <- glmnet(x, smote_data$result, family="multinomial", alpha=1,type.multinomial = "grouped" ,lambda = fit.lasso.cv$lambda.min)


```
```{r}
coef(fit.lasso1)


```


##Getting the Coefficnets for Lasso 
```{r}
c = coef(fit.lasso1,s=fit.lasso.cv$lambda.1se)
  inds <- which(c$'c-CS-m'!=0)
  imp_attributes_lasso <- row.names(c)[inds]
  imp_attributes_lasso<- imp_attributes_lasso[-c(grep("Intercept",imp_attributes_lasso))]
  imp_attributes_lasso
  c
```
#Prediction on Lasso
```{r}
xtest<-model.matrix(test_data$result~.,test_data)
pre1<-predict(fit.lasso1,xtest,type="class")


```

```{r}
confusionMatrix(pre1,test_data$result)
ytest<-test_data$result


xtrain<-model.matrix(smote_data$result~.,smote_data)
pre1<-predict(fit.lasso1,xtrain,type="class")
confusionMatrix(pre1,smote_data$result)

```

##ridge
```{r}
fit.ridge <- glmnet(x, smote_data$result, family="multinomial", alpha=0)


```
##Cross Validated Model

```{r}
fit.ridge.cv <- cv.glmnet(x,smote_data$result, type.measure="mse", alpha=0, 
                          family="multinomial",nfolds=10,parallel=TRUE)

```
Run the model taking the lambda min 

```{r}
plot(fit.ridge.cv)
lasso <- fit.ridge.cv$lambda.min
```
##ridge coefficients
```{r}
c= coef(fit.ridge.cv,s=fit.ridge.cv$lambda.1se)
inds <- which(c$`c-CS-m`!=0)
  imp_attributes_ridge<- row.names(c$`c-CS-m`)[inds]
  imp_attributes_ridge<-imp_attributes_ridge[-c(grep("Intercept",imp_attributes_ridge))]
  imp_attributes_ridge

```
#Prediction on Ridge Regularization 

```{r}
xtest<-model.matrix(test_data$result~.,test_data)
pre1<-predict(fit.ridge.cv,xtest,type="class")
confusionMatrix(pre1,test_data$result)
ytest<-test_data$result


xtrain<-model.matrix(smote_data$result~.,smote_data)
pre1<-predict(fit.ridge.cv,xtrain,type="class")
confusionMatrix(pre1,smote_data$result)
```
##elastic.net
```{r}
fit.elastic <- glmnet(x, smote_data$result, family="multinomial", alpha=0.5)
```
##Cross Validated Model

```{r}
fit.elnet.cv <- cv.glmnet(x,smote_data$result, type.measure="mse", alpha=0.5, 
                          family="multinomial",nfolds=10,parallel=TRUE)
```
Re Run the model with lambda min

```{r}
plot(fit.elnet.cv)
elnet <- fit.elnet.cv$lambda.min

```
##Getting the Elastic Net attributes

```{r}
c= coef(fit.elnet.cv,s=fit.elnet.cv$lambda.1se)
inds <- which(c$`c-CS-m`!=0)
  imp_attributes_elnet<- row.names(c$`c-CS-m`)[inds]
  imp_attributes_elnet<-imp_attributes_elnet[-c(grep("Intercept",imp_attributes_elnet))]
  imp_attributes_elnet
```
#Prediction on Elastic Net Regression 

```{r}
xtest<-model.matrix(test_data$result~.,test_data)
pre1<-predict(fit.elnet.cv,xtest,type="class")
confusionMatrix(pre1,test_data$result)
ytest<-test_data$result


xtrain<-model.matrix(smote_data$result~.,smote_data)
pre1<-predict(fit.elnet.cv,xtrain,type="class")
confusionMatrix(pre1,smote_data$result)
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```





